Evolution of Processes in Delivering Reliable Software within the European Scientific Arena

### 2019-02-13 paper-jgc.tex
Updated reference to INDIGO paper published in 2018

The {\sl INDIGO--DataCloud} (INtegrating Distributed data Infrastructures for Global
explOitation, Apr 2015 -- Sep 2017) \cite{cordis:indigo} is the last
project of software development considered in this paper. The project addressed
the existing gaps at the Cloud Platform--as--a--Service (PaaS) and Software--as--a--Service (SaaS) levels,
helping developers, e--Infrastructure administrators and scientific communities to exploit
Cloud computing benefits.

@@

\bibitem{cordis:indigo}
D. Salomoni \emph{et al.},
``INDIGO-DataCloud: A data and computing platform to facilitate seamless access to e-infrastructures,''
\emph{CoRR},
vol. abs/1711.01981, 2018.
[Online]. Available: \url{http://arxiv.org/abs/1711.01981}.
[Accessed 4 Jun. 2018].

>>>>

The {\sl INDIGO--DataCloud} (INtegrating Distributed data Infrastructures for Global
explOitation, Apr 2015 -- Sep 2017) \cite{salomoni2018indigo} is the last
project of software development considered in this paper. The project addressed
the existing gaps at the Cloud Platform--as--a--Service (PaaS) and Software--as--a--Service (SaaS) levels,
helping developers, e--Infrastructure administrators and scientific communities to exploit
Cloud computing benefits.

@@

\bibitem{salomoni2018indigo}
D. Salomoni \emph{et al.},
``Indigo-datacloud: a platform to facilitate seamless access to e-infrastructures,''
\emph{J. Grid Comp.},
vol. 16, no. 3, pp. 381--408, 2018.
